\documentclass[char]{Extinction-Level-Event}
\parindent=0pt
\begin{document}
\name{\cBandMemberOne{}}

You are a Saurene operative, a descendant of the dinosaurs, who most certainly did NOT get killed by a giant asteroid. The Saurenes are generally a peaceful people, who live in green, verdant cities that are virtually utopic. However, as every Saurene knows, a threat to your kin will bring out the lizard brain. Feral incidents are generally swept under the rug, but as an operative, you have been trained since your youth to use them to your advantage. You can call the beast within you, and it will obey, unless you are truly pushed to your limits.

For thousands of years, Saurene society has flourished. But then the flashes began, about a year ago. TIME flashes. The entire world would \emph{flicker}, and millions would see visions of another world, another now. A world in which apes had become intelligent like you, with skins of brown and pink and hair covering their flesh. Not a single scale. You could see them, like ghosts, but they couldn't see you. The world was horrified. And the flashes only got longer and longer. That's when the high council called upon you for your vulgar skills. It was time for you to be useful.

The council's top scientists have spent nearly every waking moment since the flashes began trying to work out what was going on. And they'd finally had a breakthrough. They'd figured out that this "other now" that everyone had been seeing for the past year was an alternate timeline originating 65 million years ago. You'd heard rumors since childhood that the high council's scientists had been experimenting with technology to observe the past, but it was all either highly classified or just a rumor. The scientists told you that some sort of traumatic event had occurred far in the past, likely the result of some sort of temporal manipulation. During some of the longer flashes, they had been able to access the history books of the "other now." They mentioned an asteroid killing the dinosaurs 65 million years ago, allowing the mammals to evolve and conquer Terra, which they called Earth. 

But an asteroid on its own couldn't cause timelines to collide, as they explained to you. Something else caused this, and if this were allowed to continue, your peaceful world would be consumed by this rogue timeline. They couldn't allow that to happen, so they chose you to save the world.

Saurene computational scientists had managed to crack their five most spoken languages in mere months, and built a universal translator in another month. You were given that first, a ring that allowed you to speak and understand the apes' languages as long as you had it on. But this was nothing compared to the next thing they gave you. You were entrusted with the culmination of Saurene temporal research: a personal time travel device, disguised as a scale necklace.

\begin{itemz}[Goals]
	\item 
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cTest{}} <- This is the format for contacts 
\end{contacts}

\end{document}
